---
title: "Model run report"
author: "Modeler: `r modeler`"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Model inputs

## View INLA object
**Summary of INLA object:**

```{r, echo=FALSE}
summary(model_knn)
#plot(model_knn, coords = coordinates(as(spatdata_sf, 'Spatial')))
```

**Interpretation:**
+ *n* is the size of the graph (e.g. the number of areal units)
+ *nnbs* are the number of neighbors for each node.
+ *ncc* is about connected components of the graph and this tells us how many are in the list (e.g. only 1)
+ The summary (names) tells us the possible number of neighbors per node
+ The summary (count) tells us how many counties have each number of neighbors.
+ **Note** that the `symmetry = T` above is what forced some counties to have > 4 neighbors__

# Model outputs

## INLA Object summary

```{r}
summary(m1)
```

**Interpretation of model output summary:**

+ Baseline risk in 2007 for the control group is `r round(exp(m1$summary.fixed$mean[1]), digits = 4) * 1000` *preterm births* per 1,000 live births.

## Mapping model posterior

+ These are the relative deviations of each county from the global average preterm birth rate controlling for time trend and race.

```{r}
tm_shape(spatdata_sp) +
  tm_fill('m1_iid_re',
          style = 'quantile',
          palette = 'div',
          midpoint = 1) +
  tm_borders()
```



# Observed vs Modeled 

## Raw (pooled) vs modeled rates
```{r}
input_map <- tm_shape(spatdata_sf) +
  tm_fill('ptb',
          style = 'quantile') +
  tm_borders() +
  tm_layout(title = "Raw Pooled Rates")

output_map <- tm_shape(spatdata_sf) +
  tm_fill('m1_fit',
          style = 'quantile') +
  tm_borders() +
  tm_layout(title = "Modeled Pooled Rates")

#side by side
tmap_arrange(input_map, output_map, ncol = 2)


```


